The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-07-13 paper/paper.tex
Updating results

$13\unit{Gyr}$\editremark{checkme again - a little hacky}; that said,  our conclusions are not sensitive to this choice.

@@

The close agreement between the two galaxies' binary black hole populations, determined by the anticorrelation between
star formation rate and metallicity, may be a single example of a broad trend.  This anticorrelation could cause
galaxies with similar present-day properties to always have similar present-day binary black hole populations,
regardless of their detailed assembly histories.
However, it is also possible that this close agreement is entirely a
a numerical coincdence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
  are well within the scatter around the mass-metallicity relation.  Marginally different realizations of these
  histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
  present-day properties.   \editremark{Do we have more examples?}

@@

\begin{table}
\begin{centering}
\begin{tabular}{llllc}\hline
\text{Simulation}  &  \text{BHBH} &  \text{BHNS}  & \text{NSNS} & M$_* (\msun)$\\
\hline
\hline
 \text{\BoringGalaxy} & 0.012  &0.000219 & 0.000206 & $4.24 \times 10^{10}$ \\
 \text{\ExcitingGalaxy}  & 0.0116 & 0.000264 &   0.000228 & $4.46 \times 10^{10}$ \\
 \text{\DwarfOne} & 0.0207  & 0.000275 &  & $7.8 \times 10^9$ \\
 \text{\DwarfTwo}  & 0.0524 & 0.000235  &  & $2.5 \times 10^8$ \\
\hline
\end{tabular}
\end{centering}
\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
  discussed, along with the stellar mass of each galaxy.  
}
\end{table}

@@

%Our calculations suggest that because of the often-long delays between formation and merger, combined with the
%propensity of low-metallicity gas to play an exceptionally significant role, unusually detailed information about each host galaxy could be required to realize the full
%potential of  associations between gravitational wave sources and their candidate host galaxies.
%
Fortunately,  with the advent of
IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of individual gas packets at different points in a galaxy.  
These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and chemical evolution history.    Obtaining the galaxy-wide evolutionary history can help us infer compact binary formation conditions by identifying the lowest-metallicity formation events using stellar archaeological techniques.

@@

% POINT: 
Thus, despite the challenges involved in obtaining sufficient statistics, possibly requiring third-generation instruments to
obtain sufficiently many associations, past experience suggests  host galaxy associations
will provide unique clues into the formation mechanism of compact binaries.
% 
Each host galaxy associates a merger to a unique star formation history and metallicity distribution.
With many events, these associations can potentially determine the ``response function'' for compact binaries: how often star forming gas of a given metallicity evolves into
merging compact binaries.    
%
For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M};
\citet{2010AJ....140.1557L}) has been directly measured.  % , short GRB (\editremark{XXX}), or SN has been directly measured.
%
The precise host offset can be compared to the distribution of light and star formation  \citep{2010ApJ...708....9F}.
%
Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for
% long GRBs (\editremark{XXX}), 
short GRBs \citep{2010ApJ...725.1202L}
 and
  SN Ia \citep{2011MNRAS.412.1508M}; see, e.g., the review in  \cite{2014ARAA..52...43B}.  \jillianremark{RICHARD THIS LAST PARAGRAPH IS STILL SUPER CONFUSE TO ME SORRY.  I think you need to call me and tell me about this response function so I can reword into normalpeople language}
%
%The future of gravitational wave host galaxy associations is bright.

@@

\begin{acknowledgements}
ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee.
%
JB acknowledges generous support  from the Helen Gurley Brown Trust.

>>>>

$13\unit{Gyr}$; that said,  our conclusions are not sensitive to this choice.

@@

The close agreement between the two galaxies' binary black hole populations, determined by the anticorrelation between
star formation rate and metallicity, may be a single example of a broad trend.  This anticorrelation could cause
galaxies with similar present-day properties to always have similar present-day binary black hole populations,
regardless of their detailed assembly histories.
However, it is also possible that this close agreement is entirely a
a numerical coincdence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
  are well within the scatter around the mass-metallicity relation.  Marginally different realizations of these
  histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
  present-day properties.  \editremark{but: do more examples show dramatic differences, or comparable changes}

@@

\begin{table}
\begin{centering}
\begin{tabular}{llllc}\hline
\text{Simulation}  &  \text{BHBH} &  \text{BHNS}  & \text{NSNS} & M$_* (\msun)$\\
\hline
\hline
 \text{\BoringGalaxy} & 0.0224 & 0.000247 & 0.000206  & $4.24 \times 10^{10}$ \\
 \text{\ExcitingGalaxy}  &0.0216 & 0.000297 & 0.000228 & $4.46 \times 10^{10}$ \\
 \text{\DwarfOne} &  0.0381 & 0.000308 & 0.000441& $7.8 \times 10^9$ \\
 \text{\DwarfTwo}  & 0.0949 & 0.000257 & 0.000884& $2.5 \times 10^8$ \\
 \text{h239}  &  0.023 &X & 0.000268 & \\
 \text{h285} &  0.0236 & X & 0.000241 & \\
\hline
\end{tabular}
\end{centering}
\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
  discussed, along with the stellar mass of each galaxy.  
}
\end{table}

@@

%Our calculations suggest that because of the often-long delays between formation and merger, combined with the
%propensity of low-metallicity gas to play an exceptionally significant role, unusually detailed information about each host galaxy could be required to realize the full
%potential of  associations between gravitational wave sources and their candidate host galaxies.
%
Fortunately,  with the advent of
IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of individual gas packets at different points in a galaxy.  
These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
chemical evolution history.    Obtaining the galaxy-wide evolutionary history can help us infer compact binary formation
conditions by identifying the lowest-metallicity formation events using stellar archaeological techniques.  
These techniques have been applied with great success to other transient events. 
For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M};
\citet{2010AJ....140.1557L}) has been directly measured.  % , short GRB (\editremark{XXX}), or SN has been directly measured.
%
The precise host offset can be compared to the distribution of light and star formation  \citep{2010ApJ...708....9F}.
%
Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for
% long GRBs (\editremark{XXX}), 
short GRBs \citep{2010ApJ...725.1202L}
 and
  SN Ia \citep{2011MNRAS.412.1508M}; see, e.g., the review in  \cite{2014ARAA..52...43B}.

@@

% POINT: 
Thus, despite the challenges involved in obtaining sufficient statistics, possibly requiring third-generation instruments to
obtain sufficiently many associations, past experience suggests  host galaxy associations
will provide unique clues into the formation mechanism of compact binaries.
% 
Each host galaxy associates a merger to a unique star formation history and metallicity distribution.
With many events, these associations can potentially determine the ``response function'' for compact binaries: how often star forming gas of a given metallicity evolves into
merging compact binaries.    
%
 %% \jillianremark{RICHARD THIS LAST PARAGRAPH IS STILL SUPER CONFUSE TO ME SORRY.  I think you need to call me and tell me about this response function so I can reword into normalpeople language}
%
%The future of gravitational wave host galaxy associations is bright.

@@

\begin{acknowledgements}
ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee, and PHY-1505629.
%
JB acknowledges generous support  from the Helen Gurley Brown Trust.
